module2_eco_pol_factors

### 2022-04-08 module1/moduleoneanalysis.Rmd
demographic graphs in WME

  mutate_at(vars(house), funs(case_when(. == "Hut made of mud, bamboo, straw etc. (kutcha house)" ~ 1, 
                                        . == "Permanent single story house (pukka house)" ~ 2,
                                        . == "Apartment/Flat in a multi-story building"  ~3,
                                        . == "Multi-story house" ~ 4)))

@@

```{r}
# combining quantitative livelihood-income security variables

# Livelihood security

x <- as.factor(codedmodule1$cookstove)

@@

>>>>

  mutate_at(vars(house), funs(case_when(. == "Hut made of mud, bamboo, straw etc. (kutcha house)" ~ 1, 
                                        . == "Permanent single story house (pukka house)" ~ 2,
                                        . == "Apartment/Flat in a multi-story building"  ~3,
                                        . == "Multi-story house" ~ 4))) %>%

  mutate_at(vars(foodtrouble), funs(case_when(. == "8 or more months" ~ 1,                                       
                                                          .  == "6-8 months"  ~ 2,                                                  
                                                          .  == "4-6 months"  ~ 3,                                                   
                                                          .  == "2-4 months"  ~ 4, 
                                                          .  == "1-2 months" ~ 5, 
                                                          .  == "0 months"  ~6))) %>%

   mutate_at(vars(foodadequacy), funs(case_when(. == "Extremely inadequate" ~ 1, 
                                                                        . == "Moderately inadequate" ~ 2,
                                                                        . == "Slightly inadequate" ~3,
                                                                        . == "Neither adequate nor inadequate" ~ 4,
                                                                        . == "Slightly adequate" ~ 5,
                                                                        . == "Moderately adequate" ~ 6,
                                                                        . == "Extremely adequate" ~ 7)))%>%

separate( col = cookstove, into = c("cook1", "cook2", "cook3", "cook4"), sep = ",") %>%
separate( col = vehicle, into = c("vehicle1", "vehicle2", "vehicle3", "vehicle4"), sep = ",")%>%
separate( col = foodsource, into = c("food1", "food2", "food3", "food4"), sep = ",")

@@

```{r}
# solving the problem of multiple answers  to a questions 
codedmodule1

```{r}

x <- as.factor(codedmodule1$vehicle)

@@

```{r}

```{r}

### 2022-04-08 module2/moduletwoanalysis.Rmd
demographic graphs in WME

suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(readxl))
suppressPackageStartupMessages(library(hablar))
suppressPackageStartupMessages(library(tsibble))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(DT))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(ggbiplot))

@@

codedmodule2
```

>>>>

suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(readxl))
suppressPackageStartupMessages(library(hablar))
suppressPackageStartupMessages(library(tsibble))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(DT))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(ggbiplot))
suppressPackageStartupMessages(library(readr))

@@

codedmodule2

write_csv(codedmodule2,"Macintosh HD\\Users\\prernagupta\\my documents\\codedmodule2.csv")
```
